Generating Datasets about Building Designs \\Based on a Multilayer Building Ontology

### 2015-05-01 article-01-introduction.tex
Version 1.6 (edited by Seppo)

Currently, huge amounts of building designs information is produced by 
using Building Information Modeling (BIM) tools \cite{eastman2011bim}. 
IFC \cite{ISO16739,liebich2010unveiling} -- a widely adopted standard -- provides a common representation for BIM models of 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

@@

Consequently, we convert the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}). 
New representational constructs are introduced at more comprehensive levels which, therefore, 
provide increasing detailed type information about \ifcrdf{} data (Table \ref{tab:ifcOWL-layers}).

\begin{table}
    \caption{Contents of ifcOWL layers}
    \label{tab:ifcOWL-layers}
    \centering
    \scriptsize
    \def\arraystretch{1.2}          % vertical space
    \setlength{\tabcolsep}{6pt}     % horizontal space
    \begin{tabularx}{0.95\textwidth}{|l|l|X|}
        \hline
            \textbf{Layer} & \textbf{Compatible profile} & \textbf{Contents} \\
        \hline
            ifcOWL-Simple & OWL 2 EL or & Ontology meta data plus: \\
            & OWL 2 QL or & \ \ - All basic constructs \\
            & OWL 2 RL & \ \ - All type definitions and hierarchies \\
        \hline 
            ifcOWL-Standard & OWL 2 RL & All above plus: \\
            & & \ \ - All entity type properties and keys \\
        \hline
            ifcOWL-Extended & OWL 2 RL & All above plus: \\
            & & \ \ - All cardinality constraints \\
        \hline
    \end{tabularx}
\end{table}

@@

>>>>

Currently, huge amounts of building designs information is produced
using Building Information Modeling (BIM) tools \cite{eastman2011bim}. Industry Foundation Classes 
(IFC) \cite{ISO16739,liebich2010unveiling} -- a widely adopted standard -- provides a common representation for BIM models of 
different design disciplines. All major BIM tools support IFC and can export BIM models to IFC files for exchange with other parties.

@@

Consequently, we convert the IFC schema into a \emph{flexible, multilayer \ifcowl{} ontology}
in a way that \emph{\ifcrdf{} is compatible with any of the layers} (Fig. \ref{fig:ifcOWL-layers}), and in which 
%New representational constructs are included at 
the more comprehensive levels % which, therefore, 
provide increasing detailed type information about the same \ifcrdf{} data (Table \ref{tab:ifcOWL-layers}).

\begin{table}[b]
    \caption{Contents of ifcOWL layers}
    \label{tab:ifcOWL-layers}
    \centering
    \scriptsize
    \def\arraystretch{1.2}          % vertical space
    \setlength{\tabcolsep}{6pt}     % horizontal space
    \begin{tabularx}{0.95\textwidth}{|l|l|X|}
        \hline
            \textbf{Layer} & \textbf{Compatible profile} & \textbf{Contents} \\
        \hline
            ifcOWL-Simple & OWL 2 EL or & Ontology meta data plus: \\
            & OWL 2 QL or & \ \ - All basic constructs \\
            & OWL 2 RL & \ \ - All type definitions and hierarchies \\
        \hline 
            ifcOWL-Standard & OWL 2 RL & All above plus: \\
            & & \ \ - All entity type properties and keys \\
        \hline
            ifcOWL-Extended & OWL 2 RL & All above plus: \\
            & & \ \ - All cardinality constraints \\
        \hline
    \end{tabularx}
\end{table}

@@

It should be noted that surface models targeted to building users can be shared in CityGML \cite{kolbe2005citygml}. IFC, however, provides complementary, original information about building design for a wider range of stakeholders and use cases.
%, and can also be one source when generating CityGML models.

### 2015-05-01 article-02-main.tex
Version 1.6 (edited by Seppo)

One goal in the conversion is to keep the property names simple and understandable. Therefore, domain and range constraints (specified by \name{rdfs:domain} and \name{rdfs:range}) are not included in \ifcowl{}. Firstly, there is no need to verify types or to infer types based on properties of \ifcowl{}. Secondly, while in the IFC schema the same property name can appear in multiple different classes, in RDF, property names are \emph{global} and the basic facilities given by domains and ranges do not provide any direct way to indicate that properties are \emph{local} to a class \cite{world2014rdf}. 
%Finally, direct support for such declarations is provided by OWL constructs, e.g. \name{owl:\-onProperty}.

>>>>

One goal in the conversion is to keep the property names simple and understandable. Therefore, domain and range constraints (specified by \name{rdfs:domain} and \name{rdfs:range}) are not included in \ifcowl{}. There is no need to verify types or to infer types based on properties of \ifcowl{}. Moreover, while in the IFC schema the same property name can appear in multiple different classes, in RDF, property names are \emph{global} and the basic facilities given by domains and ranges do not provide any direct way to indicate that properties are \emph{local} to a class \cite{world2014rdf}. 
%Finally, direct support for such declarations is provided by OWL constructs, e.g. \name{owl:\-onProperty}.
